---
title: "p8105_hw1_sjz2120"
output: github_document
date: "2022-09-19"
---

#Prep work
```{r load_packages}
library(tidyverse)
```

#Problem 1
```{r download_penguins_package eval = FALSE}
install.packages("palmerpenguins")
```

```{r penguins_dataset}
data("penguins", package = "palmerpenguins")

penguins
```

**Describing the penguins dataset**
*There are 8 variables in this dataset, including: Species, Island, Bill Length (in mm), Bill Depth (in mm), Flipper Length (in mm), Body Mass (in g), Sex, and Year.

*The dataset contains `nrow(penguins)` rows (`nrow(penguins)` observations) and `ncol(penguins)` columns (`ncol(penguins)` variables).

*The mean flipper length among penguins in this dataset is `mean(pull(penguins, flipper_length_mm)`.


```{r penguins_flipper_bill_scatterplot}
##Create scatterplot of flipper length (y) vs bill length (x)
ggplot(penguins, aes(x = bill_length_mm, y = flipper_length_mm, color = species)) + geom_point()

##Save scatterplot to project directory
ggsave("flipper_vs_bill_scatterplot.pdf", height = 4, width = 6)
```


#Problem 2